Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-17 paper-2023-acsos-pulverization.tex
Minors

Recent technological and scientific advances
 are extending 
 both the \emph{kinds of applications and systems} that are being addressed  
 as well as their \emph{supporting infrastructure}~\cite{DBLP:journals/iot/GillXOPBSGSWASM22}.
%
Emerging applications
 are, for instance, those based on \emph{\acp{cas}}~\cite{DBLP:journals/computer/Abowd16,DBLP:journals/sttt/NicolaJW20},
 namely collections of devices and agents
 that interact to solve problems or provide services while adapting \emph{as a whole} to dynamic environments.
%
Examples include 
  large-scale sensor-actuator networks, 
  swarms of robots,
  social computing systems,
  crowds of wearable-augmented people, and so on---supporting activities like monitoring,
  transportation, coordination, and other forms of collective intelligence~\cite{casadei2023artl-ci}.
%
Regarding infrastructure,
 it is mounting the idea of the \emph{cloud-edge continuum}~\cite{DBLP:journals/iot/BittencourtISFM18}: 
a multi-layer heterogeneous network of devices (ranging from large and powerful cloud servers to small connected \emph{things})
on which software can compute, store, and exchange data in a distributed fashion, while 
optimising for performance and resource utilisation.
%

@@

\emph{Pulverisation}~\cite{FI2020-pulverization,IEEE-IoTJ-pulverization-simulation}
 is an approach to distributed application partitioning
 and deployment, exemplified in \Cref{fig:pulv} and described in the following.
%
Its goal 
 is to provide application designers a way to specify the functional semantics of their software in a deployment-independent way.
%
To do so,
the application logic should be designed considering a \emph{logical system},
namely, a network of \emph{logical} devices forming a network with \emph{arbitrary} topology.
%
For a pulverisation system to work,
the application of every single logical device must be decomposable into an ensemble of \emph{pulverised components}
representing, respectively:
\begin{itemize}
    \item a set $\sigma$ of logical sensors;
    \item a set $\alpha$ of logical actuators;
    \item a state $\kappa$, representing the logical device's knowledge;
    \item a communication component $\chi$,
    handling interaction with reachable devices in the logical system, and
    \item a computation component $\beta$, modelling the behaviour of the logic device.
\end{itemize}
%
Decomposition of an application into pulverised components can be achieved in two ways:
either the application is designed with pulverisation in mind,
or the application is developed using a framework supporting automatic decomposition
(one notable example are aggregate computing frameworks~\cite{BealIEEEComputer2015}).
%
Once the application has been pulverised,
a mapping must be provided between the pulverised logical system and the hosts that will execute the pulverised components.
%
In this process,
a single logical component could be (and usually does) end up being executed on multiple hosts.

>>>>

Recent technological and scientific advances
 are extending 
 both the \emph{kinds of applications and systems} that are being addressed  
 as well as their \emph{supporting infrastructure}~\cite{DBLP:journals/iot/GillXOPBSGSWASM22}.
%
Emerging applications
 are, for instance, those based on \emph{\acp{cas}}~\cite{DBLP:journals/computer/Abowd16,DBLP:journals/sttt/NicolaJW20},
 namely collections of devices and agents
 that interact to solve problems or provide services while adapting \emph{as a whole} to dynamic environments.
%
Examples include 
  \ac{iot} deployments, 
  swarms of robots,
  social computing systems,
  crowds of wearable-augmented people, and so on---supporting activities like monitoring,
  transportation, coordination, and other forms of collective intelligence~\cite{casadei2023artl-ci}.
%
Regarding infrastructure,
 it is mounting the idea of the \emph{cloud-edge continuum}~\cite{DBLP:journals/iot/BittencourtISFM18}: 
a multi-layer heterogeneous network of devices (ranging from large and powerful cloud servers to small connected \emph{things})
on which software can compute, store, and exchange data in a distributed fashion, while 
optimising for performance and resource utilisation.
%

@@

\emph{Pulverisation}~\cite{FI2020-pulverization,IEEE-IoTJ-pulverization-simulation}
 is an approach to distributed application partitioning
 and deployment, exemplified in \Cref{fig:pulv} and described in the following.
%
Its goal 
 is to provide application designers a way to specify the functional semantics of their software in a deployment-independent way.
%
To do so,
the application logic should be designed considering a \emph{logical system},
namely, a network of \emph{logical} devices forming a network with \emph{arbitrary} topology.
%
For a pulverisation system to work,
the application of every single logical device must be decomposable into an ensemble of \emph{pulverised components}
representing, respectively:
\begin{itemize}
    \item a set $\sigma$ of logical sensors;
    \item a set $\alpha$ of logical actuators;
    \item a state $\kappa$, representing the logical device's knowledge;
    \item a communication component $\chi$,
    handling interaction with reachable devices in the logical system, and
    \item a computation component $\beta$, modelling the behaviour of the logic device.
\end{itemize}
%
Decomposition of an application into pulverised components can be achieved in two ways:
either the application is designed with pulverisation in mind,
or the application is developed using a framework supporting automatic decomposition
(one notable example are \emph{aggregate computing} frameworks~\cite{BealIEEEComputer2015,JLAMP2019}).
%
Once the application has been pulverised,
a mapping must be provided between the pulverised logical system and the hosts that will execute the pulverised components.
%
In this process,
a single logical component could be (and usually does) end up being executed on multiple hosts.
